---
title: "sample-resources"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sample-resources}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FHIRworks)
```


# Account  
```{r Account}
response <- get_resource_entity_set(resource = 'Account')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Account_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ActivityDefinition  
```{r ActivityDefinition}
response <- get_resource_entity_set(resource = 'ActivityDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ActivityDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# AdverseEvent  
```{r AdverseEvent}
response <- get_resource_entity_set(resource = 'AdverseEvent')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r AdverseEvent_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# AllergyIntolerance  
```{r AllergyIntolerance}
response <- get_resource_entity_set(resource = 'AllergyIntolerance')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r AllergyIntolerance_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Appointment  
```{r Appointment}
response <- get_resource_entity_set(resource = 'Appointment')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Appointment_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# AppointmentResponse  
```{r AppointmentResponse}
response <- get_resource_entity_set(resource = 'AppointmentResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r AppointmentResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# AuditEvent  
```{r AuditEvent}
response <- get_resource_entity_set(resource = 'AuditEvent')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r AuditEvent_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Basic  
```{r Basic}
response <- get_resource_entity_set(resource = 'Basic')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Basic_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Binary  
```{r Binary}
response <- get_resource_entity_set(resource = 'Binary')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Binary_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# BiologicallyDerivedProduct  
```{r BiologicallyDerivedProduct}
response <- get_resource_entity_set(resource = 'BiologicallyDerivedProduct')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r BiologicallyDerivedProduct_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# BodyStructure  
```{r BodyStructure}
response <- get_resource_entity_set(resource = 'BodyStructure')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r BodyStructure_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Bundle  
```{r Bundle}
response <- get_resource_entity_set(resource = 'Bundle')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Bundle_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CapabilityStatement  
```{r CapabilityStatement}
response <- get_resource_entity_set(resource = 'CapabilityStatement')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CapabilityStatement_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CarePlan  
```{r CarePlan}
response <- get_resource_entity_set(resource = 'CarePlan')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CarePlan_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CareTeam  
```{r CareTeam}
response <- get_resource_entity_set(resource = 'CareTeam')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CareTeam_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CatalogEntry  
```{r CatalogEntry}
response <- get_resource_entity_set(resource = 'CatalogEntry')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CatalogEntry_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ChargeItem  
```{r ChargeItem}
response <- get_resource_entity_set(resource = 'ChargeItem')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ChargeItem_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ChargeItemDefinition  
```{r ChargeItemDefinition}
response <- get_resource_entity_set(resource = 'ChargeItemDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ChargeItemDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Claim  
```{r Claim}
response <- get_resource_entity_set(resource = 'Claim')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Claim_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ClaimResponse  
```{r ClaimResponse}
response <- get_resource_entity_set(resource = 'ClaimResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ClaimResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ClinicalImpression  
```{r ClinicalImpression}
response <- get_resource_entity_set(resource = 'ClinicalImpression')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ClinicalImpression_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CodeSystem  
```{r CodeSystem}
response <- get_resource_entity_set(resource = 'CodeSystem')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CodeSystem_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Communication  
```{r Communication}
response <- get_resource_entity_set(resource = 'Communication')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Communication_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CommunicationRequest  
```{r CommunicationRequest}
response <- get_resource_entity_set(resource = 'CommunicationRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CommunicationRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CompartmentDefinition  
```{r CompartmentDefinition}
response <- get_resource_entity_set(resource = 'CompartmentDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CompartmentDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Composition  
```{r Composition}
response <- get_resource_entity_set(resource = 'Composition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Composition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ConceptMap  
```{r ConceptMap}
response <- get_resource_entity_set(resource = 'ConceptMap')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ConceptMap_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Condition (aka Problem)  
```{r Condition (aka Problem)}
response <- get_resource_entity_set(resource = 'Condition (aka Problem)')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Condition (aka Problem)_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Consent  
```{r Consent}
response <- get_resource_entity_set(resource = 'Consent')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Consent_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Contract  
```{r Contract}
response <- get_resource_entity_set(resource = 'Contract')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Contract_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Coverage  
```{r Coverage}
response <- get_resource_entity_set(resource = 'Coverage')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Coverage_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CoverageEligibilityRequest  
```{r CoverageEligibilityRequest}
response <- get_resource_entity_set(resource = 'CoverageEligibilityRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CoverageEligibilityRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# CoverageEligibilityResponse  
```{r CoverageEligibilityResponse}
response <- get_resource_entity_set(resource = 'CoverageEligibilityResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r CoverageEligibilityResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DetectedIssue  
```{r DetectedIssue}
response <- get_resource_entity_set(resource = 'DetectedIssue')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DetectedIssue_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Device  
```{r Device}
response <- get_resource_entity_set(resource = 'Device')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Device_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DeviceDefinition  
```{r DeviceDefinition}
response <- get_resource_entity_set(resource = 'DeviceDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DeviceDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DeviceMetric  
```{r DeviceMetric}
response <- get_resource_entity_set(resource = 'DeviceMetric')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DeviceMetric_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DeviceRequest  
```{r DeviceRequest}
response <- get_resource_entity_set(resource = 'DeviceRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DeviceRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DeviceUseStatement  
```{r DeviceUseStatement}
response <- get_resource_entity_set(resource = 'DeviceUseStatement')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DeviceUseStatement_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DiagnosticReport  
```{r DiagnosticReport}
response <- get_resource_entity_set(resource = 'DiagnosticReport')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DiagnosticReport_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DocumentManifest  
```{r DocumentManifest}
response <- get_resource_entity_set(resource = 'DocumentManifest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DocumentManifest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# DocumentReference  
```{r DocumentReference}
response <- get_resource_entity_set(resource = 'DocumentReference')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r DocumentReference_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EffectEvidenceSynthesis  
```{r EffectEvidenceSynthesis}
response <- get_resource_entity_set(resource = 'EffectEvidenceSynthesis')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EffectEvidenceSynthesis_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Encounter  
```{r Encounter}
response <- get_resource_entity_set(resource = 'Encounter')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Encounter_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Endpoint  
```{r Endpoint}
response <- get_resource_entity_set(resource = 'Endpoint')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Endpoint_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EnrollmentRequest  
```{r EnrollmentRequest}
response <- get_resource_entity_set(resource = 'EnrollmentRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EnrollmentRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EnrollmentResponse  
```{r EnrollmentResponse}
response <- get_resource_entity_set(resource = 'EnrollmentResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EnrollmentResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EpisodeOfCare  
```{r EpisodeOfCare}
response <- get_resource_entity_set(resource = 'EpisodeOfCare')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EpisodeOfCare_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EventDefinition  
```{r EventDefinition}
response <- get_resource_entity_set(resource = 'EventDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EventDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Evidence  
```{r Evidence}
response <- get_resource_entity_set(resource = 'Evidence')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Evidence_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# EvidenceVariable  
```{r EvidenceVariable}
response <- get_resource_entity_set(resource = 'EvidenceVariable')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r EvidenceVariable_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ExampleScenario  
```{r ExampleScenario}
response <- get_resource_entity_set(resource = 'ExampleScenario')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ExampleScenario_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ExplanationOfBenefit  
```{r ExplanationOfBenefit}
response <- get_resource_entity_set(resource = 'ExplanationOfBenefit')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ExplanationOfBenefit_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# FamilyMemberHistory  
```{r FamilyMemberHistory}
response <- get_resource_entity_set(resource = 'FamilyMemberHistory')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r FamilyMemberHistory_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Flag  
```{r Flag}
response <- get_resource_entity_set(resource = 'Flag')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Flag_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Goal  
```{r Goal}
response <- get_resource_entity_set(resource = 'Goal')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Goal_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# GraphDefinition  
```{r GraphDefinition}
response <- get_resource_entity_set(resource = 'GraphDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r GraphDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Group  
```{r Group}
response <- get_resource_entity_set(resource = 'Group')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Group_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# GuidanceResponse  
```{r GuidanceResponse}
response <- get_resource_entity_set(resource = 'GuidanceResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r GuidanceResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# HealthcareService  
```{r HealthcareService}
response <- get_resource_entity_set(resource = 'HealthcareService')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r HealthcareService_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ImagingStudy  
```{r ImagingStudy}
response <- get_resource_entity_set(resource = 'ImagingStudy')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ImagingStudy_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Immunization  
```{r Immunization}
response <- get_resource_entity_set(resource = 'Immunization')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Immunization_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ImmunizationEvaluation  
```{r ImmunizationEvaluation}
response <- get_resource_entity_set(resource = 'ImmunizationEvaluation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ImmunizationEvaluation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ImmunizationRecommendation  
```{r ImmunizationRecommendation}
response <- get_resource_entity_set(resource = 'ImmunizationRecommendation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ImmunizationRecommendation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ImplementationGuide  
```{r ImplementationGuide}
response <- get_resource_entity_set(resource = 'ImplementationGuide')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ImplementationGuide_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# InsurancePlan  
```{r InsurancePlan}
response <- get_resource_entity_set(resource = 'InsurancePlan')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r InsurancePlan_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Invoice  
```{r Invoice}
response <- get_resource_entity_set(resource = 'Invoice')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Invoice_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Library  
```{r Library}
response <- get_resource_entity_set(resource = 'Library')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Library_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Linkage  
```{r Linkage}
response <- get_resource_entity_set(resource = 'Linkage')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Linkage_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# List  
```{r List}
response <- get_resource_entity_set(resource = 'List')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r List_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Location  
```{r Location}
response <- get_resource_entity_set(resource = 'Location')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Location_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Measure  
```{r Measure}
response <- get_resource_entity_set(resource = 'Measure')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Measure_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MeasureReport  
```{r MeasureReport}
response <- get_resource_entity_set(resource = 'MeasureReport')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MeasureReport_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Media  
```{r Media}
response <- get_resource_entity_set(resource = 'Media')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Media_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Medication  
```{r Medication}
response <- get_resource_entity_set(resource = 'Medication')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Medication_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicationAdministration  
```{r MedicationAdministration}
response <- get_resource_entity_set(resource = 'MedicationAdministration')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicationAdministration_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicationDispense  
```{r MedicationDispense}
response <- get_resource_entity_set(resource = 'MedicationDispense')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicationDispense_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicationKnowledge  
```{r MedicationKnowledge}
response <- get_resource_entity_set(resource = 'MedicationKnowledge')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicationKnowledge_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicationRequest  
```{r MedicationRequest}
response <- get_resource_entity_set(resource = 'MedicationRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicationRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicationStatement  
```{r MedicationStatement}
response <- get_resource_entity_set(resource = 'MedicationStatement')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicationStatement_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProduct  
```{r MedicinalProduct}
response <- get_resource_entity_set(resource = 'MedicinalProduct')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProduct_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductAuthorization  
```{r MedicinalProductAuthorization}
response <- get_resource_entity_set(resource = 'MedicinalProductAuthorization')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductAuthorization_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductContraindication  
```{r MedicinalProductContraindication}
response <- get_resource_entity_set(resource = 'MedicinalProductContraindication')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductContraindication_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductIndication  
```{r MedicinalProductIndication}
response <- get_resource_entity_set(resource = 'MedicinalProductIndication')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductIndication_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductIngredient  
```{r MedicinalProductIngredient}
response <- get_resource_entity_set(resource = 'MedicinalProductIngredient')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductIngredient_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductInteraction  
```{r MedicinalProductInteraction}
response <- get_resource_entity_set(resource = 'MedicinalProductInteraction')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductInteraction_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductManufactured  
```{r MedicinalProductManufactured}
response <- get_resource_entity_set(resource = 'MedicinalProductManufactured')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductManufactured_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductPackaged  
```{r MedicinalProductPackaged}
response <- get_resource_entity_set(resource = 'MedicinalProductPackaged')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductPackaged_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductPharmaceutical  
```{r MedicinalProductPharmaceutical}
response <- get_resource_entity_set(resource = 'MedicinalProductPharmaceutical')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductPharmaceutical_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MedicinalProductUndesirableEffect  
```{r MedicinalProductUndesirableEffect}
response <- get_resource_entity_set(resource = 'MedicinalProductUndesirableEffect')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MedicinalProductUndesirableEffect_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MessageDefinition  
```{r MessageDefinition}
response <- get_resource_entity_set(resource = 'MessageDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MessageDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MessageHeader  
```{r MessageHeader}
response <- get_resource_entity_set(resource = 'MessageHeader')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MessageHeader_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# MolecularSequence  
```{r MolecularSequence}
response <- get_resource_entity_set(resource = 'MolecularSequence')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r MolecularSequence_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# NamingSystem  
```{r NamingSystem}
response <- get_resource_entity_set(resource = 'NamingSystem')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r NamingSystem_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# NutritionOrder  
```{r NutritionOrder}
response <- get_resource_entity_set(resource = 'NutritionOrder')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r NutritionOrder_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Observation  
```{r Observation}
response <- get_resource_entity_set(resource = 'Observation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Observation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ObservationDefinition  
```{r ObservationDefinition}
response <- get_resource_entity_set(resource = 'ObservationDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ObservationDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# OperationDefinition  
```{r OperationDefinition}
response <- get_resource_entity_set(resource = 'OperationDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r OperationDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# OperationOutcome  
```{r OperationOutcome}
response <- get_resource_entity_set(resource = 'OperationOutcome')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r OperationOutcome_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Organization  
```{r Organization}
response <- get_resource_entity_set(resource = 'Organization')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Organization_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# OrganizationAffiliation  
```{r OrganizationAffiliation}
response <- get_resource_entity_set(resource = 'OrganizationAffiliation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r OrganizationAffiliation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Parameters  
```{r Parameters}
response <- get_resource_entity_set(resource = 'Parameters')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Parameters_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Patient  
```{r Patient}
response <- get_resource_entity_set(resource = 'Patient')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Patient_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# PaymentNotice  
```{r PaymentNotice}
response <- get_resource_entity_set(resource = 'PaymentNotice')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r PaymentNotice_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# PaymentReconciliation  
```{r PaymentReconciliation}
response <- get_resource_entity_set(resource = 'PaymentReconciliation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r PaymentReconciliation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Person  
```{r Person}
response <- get_resource_entity_set(resource = 'Person')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Person_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# PlanDefinition  
```{r PlanDefinition}
response <- get_resource_entity_set(resource = 'PlanDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r PlanDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Practitioner  
```{r Practitioner}
response <- get_resource_entity_set(resource = 'Practitioner')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Practitioner_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# PractitionerRole  
```{r PractitionerRole}
response <- get_resource_entity_set(resource = 'PractitionerRole')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r PractitionerRole_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Procedure  
```{r Procedure}
response <- get_resource_entity_set(resource = 'Procedure')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Procedure_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Provenance  
```{r Provenance}
response <- get_resource_entity_set(resource = 'Provenance')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Provenance_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Questionnaire  
```{r Questionnaire}
response <- get_resource_entity_set(resource = 'Questionnaire')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Questionnaire_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# QuestionnaireResponse  
```{r QuestionnaireResponse}
response <- get_resource_entity_set(resource = 'QuestionnaireResponse')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r QuestionnaireResponse_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# RelatedPerson  
```{r RelatedPerson}
response <- get_resource_entity_set(resource = 'RelatedPerson')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r RelatedPerson_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# RequestGroup  
```{r RequestGroup}
response <- get_resource_entity_set(resource = 'RequestGroup')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r RequestGroup_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ResearchDefinition  
```{r ResearchDefinition}
response <- get_resource_entity_set(resource = 'ResearchDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ResearchDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ResearchElementDefinition  
```{r ResearchElementDefinition}
response <- get_resource_entity_set(resource = 'ResearchElementDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ResearchElementDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ResearchStudy  
```{r ResearchStudy}
response <- get_resource_entity_set(resource = 'ResearchStudy')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ResearchStudy_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ResearchSubject  
```{r ResearchSubject}
response <- get_resource_entity_set(resource = 'ResearchSubject')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ResearchSubject_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# RiskAssessment  
```{r RiskAssessment}
response <- get_resource_entity_set(resource = 'RiskAssessment')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r RiskAssessment_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# RiskEvidenceSynthesis  
```{r RiskEvidenceSynthesis}
response <- get_resource_entity_set(resource = 'RiskEvidenceSynthesis')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r RiskEvidenceSynthesis_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Schedule  
```{r Schedule}
response <- get_resource_entity_set(resource = 'Schedule')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Schedule_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SearchParameter  
```{r SearchParameter}
response <- get_resource_entity_set(resource = 'SearchParameter')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SearchParameter_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ServiceRequest  
```{r ServiceRequest}
response <- get_resource_entity_set(resource = 'ServiceRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ServiceRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Slot  
```{r Slot}
response <- get_resource_entity_set(resource = 'Slot')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Slot_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Specimen  
```{r Specimen}
response <- get_resource_entity_set(resource = 'Specimen')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Specimen_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SpecimenDefinition  
```{r SpecimenDefinition}
response <- get_resource_entity_set(resource = 'SpecimenDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SpecimenDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# StructureDefinition  
```{r StructureDefinition}
response <- get_resource_entity_set(resource = 'StructureDefinition')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r StructureDefinition_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# StructureMap  
```{r StructureMap}
response <- get_resource_entity_set(resource = 'StructureMap')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r StructureMap_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Subscription  
```{r Subscription}
response <- get_resource_entity_set(resource = 'Subscription')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Subscription_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Substance  
```{r Substance}
response <- get_resource_entity_set(resource = 'Substance')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Substance_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SubstancePolymer  
```{r SubstancePolymer}
response <- get_resource_entity_set(resource = 'SubstancePolymer')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SubstancePolymer_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SubstanceProtein  
```{r SubstanceProtein}
response <- get_resource_entity_set(resource = 'SubstanceProtein')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SubstanceProtein_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SubstanceReferenceInformation  
```{r SubstanceReferenceInformation}
response <- get_resource_entity_set(resource = 'SubstanceReferenceInformation')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SubstanceReferenceInformation_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SubstanceSpecification  
```{r SubstanceSpecification}
response <- get_resource_entity_set(resource = 'SubstanceSpecification')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SubstanceSpecification_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SubstanceSourceMaterial  
```{r SubstanceSourceMaterial}
response <- get_resource_entity_set(resource = 'SubstanceSourceMaterial')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SubstanceSourceMaterial_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SupplyDelivery  
```{r SupplyDelivery}
response <- get_resource_entity_set(resource = 'SupplyDelivery')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SupplyDelivery_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# SupplyRequest  
```{r SupplyRequest}
response <- get_resource_entity_set(resource = 'SupplyRequest')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r SupplyRequest_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# Task  
```{r Task}
response <- get_resource_entity_set(resource = 'Task')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r Task_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# TerminologyCapabilities  
```{r TerminologyCapabilities}
response <- get_resource_entity_set(resource = 'TerminologyCapabilities')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r TerminologyCapabilities_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# TestReport  
```{r TestReport}
response <- get_resource_entity_set(resource = 'TestReport')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r TestReport_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# TestScript  
```{r TestScript}
response <- get_resource_entity_set(resource = 'TestScript')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r TestScript_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# ValueSet  
```{r ValueSet}
response <- get_resource_entity_set(resource = 'ValueSet')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r ValueSet_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# VerificationResult  
```{r VerificationResult}
response <- get_resource_entity_set(resource = 'VerificationResult')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r VerificationResult_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```




# VisionPrescription  
```{r VisionPrescription}
response <- get_resource_entity_set(resource = 'VisionPrescription')
payload <- return_payload(response)
if (!is.null(payload)) {
  head(payload$resource)
}
            
```




```{r VisionPrescription_pause, echo=FALSE,eval=TRUE}
Sys.sleep(5)
```


